### 2008-03-17 SAiP/Module1/H3/doc/architecturaldesign.tex
Adding text to C&C - diagrams missing

\fixme{Answer question 4.3}

>>>>

There are four major structures in Component-and-Connector:

\begin{itemize}
  \item Process or communicating processes.
	\begin{itemize}
	  \item This structure shows the execution path through a system, and is used to give the engineer an understand about the dynamic behaviour of the system. These structures may help ingeneers increase Performance and Availability.
	\end{itemize}
  \item Concurrency.
	\begin{itemize}
	  \item This structure is used to see the parallelism in the system, or part of the system, and when a system, or part of a system, is build around this structure it promotes performance. 
	\end{itemize}
  \item Shared data or Repository
	\begin{itemize}
	  \item This is a very good structure to use to illustarte how the data is processed and consumed to/from the database (Database Facade). When a system, or part of a system, is build around this structure it promotes performance and data entegrity. 
	\end{itemize}
  \item Client-server
	\begin{itemize}
  		\item This is a very good structure to see the protocols used between the clients and the server, and the messages they communicate. When a system, or part of a system, is build around this structure it promotes seperation of concern (i.e. Modifiability) and allows for Availability tactics like Load balancing.
	\end{itemize}
\end{itemize}

\fixme{Insert diagrams for C&C}
